JD notes on effects

### 2022-07-20 manuscript/body.tex
some progress

We start by comparing our proposed approach with the existing implementations and then illustrate the construction of outcome plots and also demonstrate that the mean-based and observed-value-based approaches produce different results in models with nonlinear link functions \jd{What‽: and/or additional source(s) of potential bias}. In addition, we demonstrate that observed-value-based approach can be used for bias correction.

>>>>

We start by comparing our proposed approach with the existing implementations and then illustrate the construction of outcome plots and also demonstrate that the mean-based approach works well for interactions and multi-parameter variables, and that and observed-value approach can correct for bias induced by non-linear averaging.
